Read quality check

### 2019-02-15 writing/qual-check.Rmd
move Rmd files to writing/ and ignore the directory on Packrat; fix report knitting on UPPMAX

```{r include=FALSE}
datasets <- readd(datasets)
# xdata <- readd(itsxtrim_.its1.lr5.)
# pos <- readd(positions_pb500002A1f)
reads <- readd(qstats_join) %>%
      tidyr::extract(col = "file",
                     into = c("Seq.Run", "Plate", "Well", "Direction", "Region"),
                     regex = "([:alpha:]+_\\d+)_(\\d+)-([A-H]1?\\d)([fr]?)-([:alnum:]+)\\.trim\\.fastq\\.gz") %>%
  left_join(datasets)
```

>>>>

```{r include=FALSE}
datasets <- readd(datasets)
# xdata <- readd(itsxtrim_.its1.lr5.)
# pos <- readd(positions_pb500002A1f)
reads <- readd(qstats_join)
```
